---
title: "Simulations"
author: "Tiger Zeng"
date: "7/18/2022"
output: html_document
---

# Simulations

$X = (X_1, X_2, X_3, X_4, X_5) \sim N(0, I_5)$, $V = (X_1, X_2, X_3)$. Given $n$ samples, generate $S$ (participation probability) according to $P(S=1 | V) =  \rho(V) = 0.5$. In the source (target) population, set $\pi(x) = 0.3x_1 - 0.3x_3$ and simulate the treatment $A \sim \text{Bernoulli }(\pi(X))$. Consider linear potential outcome model

\[
\mu_1 (x) = 1.5x_1+x_4+1, \, \mu_0(x) = x_1
\]

and $Y = A\mu_1(X) + (1-A)\mu_0(X) + N(0,1)$. So we have

\[
\tau_1(v) = \mathbb{E}[\mu_1(X)|V] = 1.5x_1 +1, \tau_0(v) = x_1.
\]

And the effect is 1. The nuisance estimators are $\hat{\mu}_a(x) = \mu_a(x) + \epsilon_{1,n}, \hat{\tau}_a(v) = \tau_a(v) + \epsilon_{2,n}, \hat{\rho}(v) = \text{expit}(\text{logit}(\rho(v))+\epsilon_{3,n}), \hat{\pi}(x) = \text{expit}(\text{logit}(\pi(x))+\epsilon_{4,n})$, where $\epsilon_{i,n} \sim N(n^{-\alpha}, n^{-2\alpha})$.

```{r echo=FALSE, message=FALSE}
# Doubly robust transportation
transport_dr_simu <- function(a, y, x_source, x_target, mu1_hat = NULL, mu0_hat = NULL, pi_hat = NULL, rho_hat = NULL, tau1_hat = NULL, tau0_hat = NULL){
  n_source <- nrow(x_source)
  n_target <- nrow(x_target)
  muhat <- matrix(0, nrow=n_source, ncol=2)
  pi_source <- numeric(length=n_source)
  pi_treat <- numeric(length=n_source)
  tau_source <- matrix(0, nrow=n_source, ncol=2)
  tau_target <- matrix(0, nrow=n_target, ncol=2)
  # estimate regression function
  muhat[,1] <- mu0_hat(x_source)
  muhat[,2] <- mu1_hat(x_source)
  tau_source[,1] <- tau0_hat(x_source)
  tau_source[,2] <- tau1_hat(x_source)
  tau_target[,1] <- tau0_hat(cbind(x_target, matrix(0, nrow = n_target, ncol=2)))
  tau_target[,2] <- tau1_hat(cbind(x_target, matrix(0, nrow = n_target, ncol=2)))
  
  # estimate propensity score into source
  pi_source <- rho_hat(x_source)

  # estimate propensity score of treatment in source data
  pi_treat <- pi_hat(x_source)
  
  # Doubly robust estimation
  ifs <- matrix(0, nrow=n_source + n_target, ncol=2)
  for (aa in 1:2){
    ifs[1:n_source,aa] <- as.numeric(a == aa-1)*(1-pi_source)*(y-muhat[,aa])/(pi_source*(pi_treat^(aa-1)*(1-pi_treat)^(2-aa))) + (1-pi_source)/pi_source*(muhat[,aa] - tau_source[,aa])
    ifs[(n_source+1):(n_source+n_target),aa] <- tau_target[,aa]
  }
  ifs <- ifs/(n_target)*(n_target+n_source)
  results <- matrix(0, nrow=2, ncol=3)
  results[1,1:2] <- apply(ifs, 2, mean)
  results[1,3] <- results[1,2] - results[1,1]
  results[2,1:2] <- apply(ifs, 2, sd)/sqrt(n_source + n_target)
  results[2,3] <- sd(ifs[,2]-ifs[,1])/sqrt(n_source + n_target)
  return(results)
}

# Plug-in
transport_plugin_simu <- function(a, y, x_source, x_target, tau1_hat = NULL, tau0_hat = NULL){
  n_source <- nrow(x_source)
  n_target <- nrow(x_target)
  muhat <- matrix(0, nrow=n_source, ncol=2)
  tau_target <- matrix(0, nrow=n_target, ncol=2)
  tau_target[,1] <- tau0_hat(cbind(x_target, matrix(0, nrow = n_target, ncol=2)))
  tau_target[,2] <- tau1_hat(cbind(x_target, matrix(0, nrow = n_target, ncol=2)))
  potential_mean <- colMeans(tau_target)
  return(potential_mean)
}

# Doubly robust generalization
generalize_dr_simu <- function(a, y, x_source, x_target, mu1_hat = NULL, mu0_hat = NULL, pi_hat = NULL, rho_hat = NULL, tau1_hat = NULL, tau0_hat = NULL){
  n_source <- nrow(x_source)
  n_target <- nrow(x_target)
  muhat <- matrix(0, nrow=n_source, ncol=2)
  pi_source <- numeric(length=n_source)
  pi_treat <- numeric(length=n_source)
  tau_source <- matrix(0, nrow=n_source, ncol=2)
  tau_target <- matrix(0, nrow=n_target, ncol=2)
  # estimate regression function
  muhat[,1] <- mu0_hat(x_source)
  muhat[,2] <- mu1_hat(x_source)
  tau_source[,1] <- tau0_hat(x_source)
  tau_source[,2] <- tau1_hat(x_source)
  tau_target[,1] <- tau0_hat(cbind(x_target, matrix(0, nrow = n_target, ncol=2)))
  tau_target[,2] <- tau1_hat(cbind(x_target, matrix(0, nrow = n_target, ncol=2)))
  # estimate propensity score into source
  pi_source <- rho_hat(x_source)
  # estimate propensity score of treatment in source data
  pi_treat <- pi_hat(x_source)
  
  # Doubly robust estimation
  ifs <- matrix(0, nrow=n_source + n_target, ncol=2)
  for (aa in 1:2){
    ifs[1:n_source,aa] <- as.numeric(a == aa-1)*(y-muhat[,aa])/(pi_source*(pi_treat^(aa-1)*(1-pi_treat)^(2-aa))) + 1/pi_source*(muhat[,aa] - tau_source[,aa]) + tau_source[,aa]
    ifs[(n_source+1):(n_source+n_target),aa] <- tau_target[,aa]
  }
  results <- matrix(0, nrow=2, ncol=3)
  results[1,1:2] <- apply(ifs, 2, mean)
  results[1,3] <- results[1,2] - results[1,1]
  results[2,1:2] <- apply(ifs, 2, sd)/sqrt(n_source + n_target)
  results[2,3] <- sd(ifs[,2]-ifs[,1])/sqrt(n_source + n_target)
  return(results)
}

logit <- function(x){
  return(log(x/(1-x)))
}

expit <- function(x){
  return(1/(1+exp(-x)))
}


f_hat <- function(beta, b, epsilon){
  return(function(x) {
    return(c(x %*% beta + b + epsilon))
  })
}

prob_hat <- function(beta, b, epsilon){
  return(function(x) {
    return(expit(c(x %*% beta + b + epsilon)))
  })
}

data_generator <- function(beta1_y, beta0_y, beta_pi, n, rho){
  s <- rbinom(n, 1, rho)
  n1 <- sum(s)
  n2 <- n-n1
  x_source <- matrix(rnorm(n1*5), ncol=5)
  x_target <- matrix(rnorm(n2*3), ncol=3)
  # x_target[,1] <- x_target[,1] + 1
  colnames(x_source) <- paste0("X", 1:5)
  colnames(x_target) <- paste0("X", 1:3)
  a <- rbinom(n1, 1, expit(x_source %*% beta_pi))
  y <- (1-a)*(x_source%*%beta0_y) + a*(x_source%*%beta1_y+1)+rnorm(n1)
  return(list(a=a, y=c(y), x_source=x_source, x_target=x_target))
}

M <- 1000
n <- 100
rho <- 0.5
alphas <- seq(from = 0.1, to = 0.5, by=0.05)
beta1_y <- c(1.5, 0, 0, 1, 0)
b <- 1
beta0_y <- c(1, 0, 0, 0, 0)
beta_pi <- c(0.3, 0, -0.3, 0, 0)
results_dr <- matrix(0, ncol = M, nrow = length(alphas))
results_plg <- matrix(0, ncol = M, nrow = length(alphas))
set.seed(521)
for(alpha in seq_along(alphas)){
  for (m in 1:M){
    #set.seed(alpha+m*100)
    dat <- data_generator(beta1_y, beta0_y, beta_pi, n ,rho)
    mu1_hat <- f_hat(beta1_y, b, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    mu0_hat <- f_hat(beta0_y, 0, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    rho_hat <- prob_hat(rep(0,5), 0, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    tau1_hat <- f_hat(c(1.5, 0, 0, 0, 0), 1, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    tau0_hat <- f_hat(c(1, 0, 0, 0, 0), 0, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    pi_hat <- prob_hat(beta_pi, 0, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    res_dr <- transport_dr_simu(dat$a, dat$y, dat$x_source, dat$x_target, mu1_hat=mu1_hat, mu0_hat=mu0_hat, rho_hat=rho_hat, tau1_hat=tau1_hat, tau0_hat=tau0_hat, pi_hat=pi_hat)
    results_dr[alpha, m] <- res_dr[1,2]
    res_plg <- transport_plugin_simu(dat$a, dat$y, dat$x_source, dat$x_target, tau1_hat = tau1_hat, tau0_hat = tau0_hat)
    results_plg[alpha, m] <- res_plg[2]
  }
}
dr1 <- sqrt(apply((results_dr-1)^2, 1, mean))
plg1 <- sqrt(apply((results_plg-1)^2, 1, mean))
plot(x = alphas, y = dr1, main = "n=100", ylim = range(c(dr1, plg1)), ylab = "RMSE", cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5)
lines(x = alphas, y = dr1)
points(x = alphas, y = plg1, col = "red")
lines(x = alphas, y = plg1, col = "red", lty=2)
legend("topright", c("DR", "Plug-in"), lty=1:2, pch=c(1,1), col=c("black", "red"), cex=1.5)
```

```{r echo=FALSE}
M <- 1000
n <- 1000
rho <- 0.5
alphas <- seq(from = 0.1, to = 0.5, by=0.05)
beta1_y <- c(1.5, 0, 0, 1, 0)
b <- 1
beta0_y <- c(1, 0, 0, 0, 0)
beta_pi <- c(0.3, 0, -0.3, 0, 0)
results_dr <- matrix(0, ncol = M, nrow = length(alphas))
results_plg <- matrix(0, ncol = M, nrow = length(alphas))
set.seed(521)
for(alpha in seq_along(alphas)){
  for (m in 1:M){
    # set.seed(alpha*100+m*10)
    dat <- data_generator(beta1_y, beta0_y, beta_pi, n ,rho)
    mu1_hat <- f_hat(beta1_y, b, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    mu0_hat <- f_hat(beta0_y, 0, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    rho_hat <- prob_hat(rep(0,5), 0, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    tau1_hat <- f_hat(c(1.5, 0, 0, 0, 0), 1, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    tau0_hat <- f_hat(c(1, 0, 0, 0, 0), 0, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    pi_hat <- prob_hat(beta_pi, 0, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    res_dr <- transport_dr_simu(dat$a, dat$y, dat$x_source, dat$x_target, mu1_hat=mu1_hat, mu0_hat=mu0_hat, rho_hat=rho_hat, tau1_hat=tau1_hat, tau0_hat=tau0_hat, pi_hat=pi_hat)
    results_dr[alpha, m] <- res_dr[1,2]
    res_plg <- transport_plugin_simu(dat$a, dat$y, dat$x_source, dat$x_target, tau1_hat = tau1_hat, tau0_hat = tau0_hat)
    results_plg[alpha, m] <- res_plg[2]
  }
}
dr1 <- sqrt(apply((results_dr-1)^2, 1, mean))
plg1 <- sqrt(apply((results_plg-1)^2, 1, mean))
plot(x = alphas, y = dr1, main = "n=1000", ylim = range(c(dr1, plg1)), ylab = "RMSE", cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5)
lines(x = alphas, y = dr1)
points(x = alphas, y = plg1, col = "red")
lines(x = alphas, y = plg1, col = "red", lty=2)
legend("topright", c("DR", "Plug-in"), lty=1:2, pch=c(1,1), col=c("black", "red"), cex=1.5)
```

```{r echo=FALSE}
M <- 1000
n <- 5000
rho <- 0.5
alphas <- seq(from = 0.1, to = 0.5, by=0.05)
beta1_y <- c(1.5, 0, 0, 1, 0)
b <- 1
beta0_y <- c(1, 0, 0, 0, 0)
beta_pi <- c(0.3, 0, -0.3, 0, 0)
results_dr <- matrix(0, ncol = M, nrow = length(alphas))
results_plg <- matrix(0, ncol = M, nrow = length(alphas))
set.seed(521)
for(alpha in seq_along(alphas)){
  for (m in 1:M){
    # set.seed(alpha*1000+m*10)
    dat <- data_generator(beta1_y, beta0_y, beta_pi, n ,rho)
    mu1_hat <- f_hat(beta1_y, b, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    mu0_hat <- f_hat(beta0_y, 0, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    rho_hat <- prob_hat(rep(0,5), 0, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    tau1_hat <- f_hat(c(1.5, 0, 0, 0, 0), 1, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    tau0_hat <- f_hat(c(1, 0, 0, 0, 0), 0, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    pi_hat <- prob_hat(beta_pi, 0, rnorm(1, mean=n^(-alphas[alpha]), sd = n^(-alphas[alpha])))
    res_dr <- transport_dr_simu(dat$a, dat$y, dat$x_source, dat$x_target, mu1_hat=mu1_hat, mu0_hat=mu0_hat, rho_hat=rho_hat, tau1_hat=tau1_hat, tau0_hat=tau0_hat, pi_hat=pi_hat)
    results_dr[alpha, m] <- res_dr[1,2]
    res_plg <- transport_plugin_simu(dat$a, dat$y, dat$x_source, dat$x_target, tau1_hat = tau1_hat, tau0_hat = tau0_hat)
    results_plg[alpha, m] <- res_plg[2]
  }
}
dr1 <- sqrt(apply((results_dr-1)^2, 1, mean))
plg1 <- sqrt(apply((results_plg-1)^2, 1, mean))
plot(x = alphas, y = dr1, main = "n=5000", ylim = range(c(dr1, plg1)), ylab = "RMSE", cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5)
lines(x = alphas, y = dr1)
points(x = alphas, y = plg1, col = "red")
lines(x = alphas, y = plg1, col = "red", lty=2)
legend("topright", c("DR", "Plug-in"), lty=1:2, pch=c(1,1), col=c("black", "red"), cex=1.5)
```






